\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDE

### 2015-03-04 paper_draft1.tex
outline 1

%\begin{center}
\title{\bf Adaptive Mesh Refinement for Hyperbolic PDE}
\author{}
\maketitle
%\end{center}

@@

\section{Outline}
\begin{itemize}
\item

>>>>

%\begin{center}
\title{\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDE}
\author{}
\maketitle
%\end{center}

@@

\section{Outline}
\begin{itemize}
\item Overview of paper
\begin{itemize}
\item Description of AMR, Figure 2.1 from Berger-Leveque paper.
\item Wave propagation form for 1-d equations. Updating on grid interfaces, section 4 of paper
\item pseudo-code for algorithm, similar to that on page 2310 of paper.
\item notes on: flagging cells, boundary conditions
\end{itemize}
\item Examples:
\begin{itemize}
\item scalar advection
\item linear system (e.g. Acoustics)
\item variable coefficient (e.g. Color equation)
\item nonlinear scalar (burgers)
\item nonlinear system (shallow water or acoustics with pressure term)
\end{itemize}
